Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
Intro to ALG3

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2$ and $C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that upper bounds the cost of a~single repartition of \TAlg.

@@

\begin{theorem}
	\TAlg is $60\ell$-competitive for $k=3$.
\end{theorem}
\begin{proof}
	Fix a~completed phase, and consider the state of \TAlg's counters at the end of it (before the reset).
	We consider the incomplete phase later in this proof.

@@

\begin{proof}%[Proof of Theorem \ref{thm:k=2}]
	Fix an input sequence of requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter,
	i.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a~pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

>>>>

\begin{theorem}
	\TAlg is $60\ell$-competitive for $k=3$.
	\label{thm:k=3}
\end{theorem}

@@

Before bounding the competitive ratio of \TAlg, we introduce the lemma that upper bounds the cost of a~single repartition of \TAlg.
In our analysis, we distinguish among three types of clusters: $C_1, C_2$ and $C_3$. In a~cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.

@@

\begin{proof}[Proof of Theorem \ref{thm:k=3}]
	Fix a~completed phase, and consider the state of \TAlg's counters at the end of it (before the reset).
	We consider the incomplete phase later in this proof.

@@

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Fix an input sequence of requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter,
	i.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a~pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.
